% Chicken with sweet potato recipe
\begin{recipe}
[
    preparationtime = 10 min,
    bakingtime = 25 min,
    portion = \portion{2},
]{Chicken with Sweet Potatos}

    \introduction
    {
        First put water with salt to boil in a sauce pan. Just before the water boils, peel the skin of the sweet potatoes and cut to bite-sized pieces. You have to put the sweet potatoes to the boiling water immediately, because once peeled it is discoloured quickly. Also chicken breasts should be skinless and boneless.
    }
    
    \ingredients
    {
        \unit[250]{g} & Sweet Potatoes\\
        \unit[100]{g} & Spinach or Rocket \\
        1 tbsp & Olive Oil \\
        2 & Chicken Breasts \\
        0.5 large & Onion, cut into wedges \\
        Some & Curry \\
        & Basil \\
        & Thyme \\
        & Rosemary \\
        or & \\
        2 tbsp & Rogan Josh Curry Paste \\
        0.5 tsp & Black pepper
    }   
    
    \preparation
    {
        \step Cook the sweet potatoes in the salted, boiling water for 5-7 minutes until just tender. Drain well, keeping 120ml of the water in a glass for later use, and set potatoes aside. While potatoes are cooking, heat the oil in a large frying pan, and then add the chicken breasts and the onions.
        \step Cook the chicken for 5-6 minutes, then turn the other side and cook for another 3-4 minutes, until chicken is browned on both sides and cooked through. Sprinkle the curry, basil, thyme, rosemary or stir in the curry paste and black pepper and cook for 1 more minute. Add the tomatoes and cook for another minute.
        \step Pour in the boiling water kept from sweet potatoes and mix well. Turn down the heat and simmer for 4-5 minutes covered, turning sides half way through. Then optionally add the spinach or rocket and cook for 1-2 minutes until wilted. Finally add the drained potatoes and heat through.
    }
    
    \suggestion[Serving Suggestion]
    {
        You can serve along with some black rice (best taste) or brown rice.
    }
\end{recipe}

\pagebreak  % Page break to the next recipe