% Orzo recipe
\begin{recipe}
[
    preparationtime = 10 min,
    bakingtime = 20 min,
    portion = \portion{1},
]{Orzo with Mushrooms}

    \introduction
    {
        Generally for whole wheat orzo, use \unit[275]{ml} of water per \unit[100]{g} of orzo. Add \unit[25]{ml} more water for each \unit[100]{g} of orzo, if water hungry ingredients, like mushrooms, are used. This is a recipe for one portion, but it scales to larger portions, with the same rules.
    }
    
    \ingredients
    {
        \unit[300]{ml} & Water \\
        \unit[100]{g} & Whole wheat orzo\\
        \unit[80]{g} & Mini mushrooms, sliced \\
        1 & Vegetable broth cube \\
        0.5 large & Onion, chopped \\
        1 tbsp & Olive oil \\
        0.25 cup & Tomato sauce \\
        Some & Basil \\
        & Thyme \\
        & Rosemary \\
        & Black pepper \\
        & Parsley, chopped \\
        & Dill, chopped
    }   
    
    \preparation
    {
        \step In a small pan bring the water to a boil and add the vegetable broth cube, basil, thyme, rosemary, black pepper and the sliced mushrooms. Cook for 2-3 minutes, just to the point where mushrooms are starting to get tender.
        \step While cooking the mushrooms, heat in a sauce pan the olive oil and saute the onions until they have a golden brown look.
        \step Once onions are sauteed, add the orzo and mix well until is all covered with the oil. Then add the tomato sauce and mix well until all orzo is covered with the tomato sauce.
        \step Then pour the boiling water from the small pan, lower the heat and cook for 5-8 minutes, uncovered, stirring frequently. Remove from heat once the liquid has thickened enough and it barely covers the orzo. Add the parsley and dill and mix well.
        \step Let it settle at least 15 minutes, before stirring and serving. Always stir well before serving. Leftovers can be refrigerated up to 3-4 days.
    }
    
    \suggestion[Serving Suggestion]
    {
        It can be very well served with chicken.
    }
\end{recipe}

\pagebreak